SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 conc.tex
Mostly related to images, methodology, typos etc
Small changes throughout the paper
Update conc.tex

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce perceptron-based learning for prefetching.  The
perceptron filter acts independently as a check on the underlying prefetch
engine.  PPF improves performance over the base prefetcher by 11.9\%.  We
believe that this is a robust and adaptable technique that can be used to
enhance any existing and upcoming prefetchers.

>>>>

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce Perceptron-Based Prefetch Filtering (PPF). PPF 
acts as an independent check on the quality of predictions made by the
underlying prefetch engine.  We evaluate PPF in the context of using SPP
as the baseline prefetch engine, but in principle other prefetchers could
be used.  PPF is so effective at filtering bad prefetches, that it enables
prefetcher design to focus more on increasing coverage, and allows existing
prefetchers to be re-tuned for higher coverage.  PPF improves performance 
over the base prefetcher by up to 11.4\%. We believe that PPF is a robust
and adaptable technique that can be used to enhance any existing prefetchers
and can be a valuable tool in the design of future prefetchers.
